### 2016-10-05 robust-software.tex
Setting defaults

\item
Find somewhere to say, ``Check that all input values are in a reasonable range,
choose reasonable defaults where possible,
and no defaults at all otherwise.''

@@

>>>>

@@

Finally,
if the software is configurable in any way,
it should \textbf{check that all input values are in a reasonable range},
\textbf{choose reasonable defaults where they exist},
and \textbf{set no defaults at all when there aren't any reasonable ones}.
Software should also \textbf{check that configuration values are reasonable at startup}:
few things are as annoying as having a program announce after running for two hours
that it isn't going to save its results
because the requested directory doesn't exist.
